---
Author: "Aniket Chakraborty"
at Updated:"07.06.2023 or 7th June 2023"
title: "R Notebook on Simple and Multiple Linear Regression Model"
output: html_notebook
---
# Installing and loading required packages
```{r}
install.packages("tidyverse")
install.packages("car")
library(car)
library(tidyverse)
library(dplyr)
```

# Reading the file Food_Texture_Data.csv using read.csv()function
```{r}
food_df_01 <- read.csv("Food_Texture_Data.csv")
```

# Previewing the data frame using View()function
```{r}
View(food_df_01)
```

# Checking first few rows of the data set
```{r}
head(food_df_01,5)
```
# Adding a new column called Price and storing it in a data frame
```{r}
food_df_02 <- food_df_01 %>% mutate(Price=80*(Density/(Crispy+Oil+Fracture+Hardness)))
head(food_df_02,5)
```
# Renaming some variables for ease of using them and storing them in a new data frame
```{r}
food_df_03 <- food_df_02 %>% rename(Oil_Percentage=Oil)
head(food_df_03)
```
# Creating the final data frame to work on it further by deselcting the 'X' variable
```{r}
food_data <- food_df_03 %>% select(-X)
head(food_data)
```
# Previewing the food_data data frame
```{r}
View(food_data)
```

#                            Building a simple linear regression model 

# Price as response and Oil_Percentage as predictor variable. Here we use the lm() function to build the model
```{r}
model1 <- lm(data=food_data, Price ~ Oil_Percentage)
summary(model1)
```
# Price as response and Density as predictor variable. Here we use the lm() function to build the model
```{r}
model2 <- lm(data=food_data,Price ~ Density)
summary(model2)
```

# Price as response and Crispy as predictor variable. Here we use the lm() function to build the model
```{r}
model3 <- lm(data=food_data,Price ~ Crispy)
summary(model3)
```

# Price as response and Hardness as predictor variable. Here we use the lm() function to build the model
```{r}
model4 <- lm(data=food_data, Price ~ Hardness)
summary(model4)
```

# Price as response and Fracture as predictor variable. Here we use the lm() function to build the model
```{r}
model5 <- lm(data=food_data, Price ~ Fracture)
summary(model5)
```
#                      Building a Multiple Linear regression Model

# price as response variable and the other variables as predictor variables
```{r}
model6 <- lm(data=food_data, Price ~ Oil_Percentage+Density+Hardness+Crispy+Fracture)
summary(model6)
```
# All the interpreations of models that are build are given in detail in a separate Markdown File.It contains basic notations, basic terminologies and other things. The concept of being confounding and collinear is also covered in that discussion.

# Checking the coefficient correlation matrix to know which factor effects the most in predicting the Price. We will discuss this matrix later in detail in the markdown document.
```{r}
round(cor(food_data[c("Oil_Percentage","Density","Hardness","Fracture","Crispy")]),2)
```
# Now here VIF (Variance Inflation Factor) is calculated for the predictor variables. Here we observe that the VIF value is the highest for the variable Crispy (>5). So we eliminate it and build the model with the other features.
```{r}
car::vif(model6)
```
# Building model considering all but expect Crispy as predictor variable
```{r}
model7 <- lm(data=food_data, Price ~ Oil_Percentage+Density+Hardness+Fracture)
summary(model7)
```
# Here to check collinearity we crate a new column called Density_in_hundred and store it in a new data frame
```{r}
food_data_1 <- food_data %>% mutate(Density_in_hundred = Density/100)
head(food_data_1,5)
```
# Now we build a Multiple Linear Regression Model with Price as response and Density and Density_in_hundred and Hardness as predictor
```{r}
model8 <- lm(data=food_data_1, Price ~ Density+Hardness+Density_in_hundred)
summary(model8)
```
# Getting the mean of Price
```{r}
mean(food_data$Price)
```

# Now to know what happens in the result if there are categorical predictors, we create a column called Costly(Yes and No) Depending on the price and store it in a new data frame
```{r}
food_data_final <- food_data_1 %>% mutate(Costly=ifelse(Price>mean(Price),"Yes","No"))
head(food_data_final)
```
# Previewing the latest data frame
```{r}
View(food_data_final)
```

# Now make a model with Price as response variable and Density, Hardness and Costly as predictor variables
```{r}
model9 <- lm(data=food_data_final, Price ~ Density+Hardness+Costly)
summary(model9)
```










